\chapter{Linear Transformations}

We want mappings that preserve linear combinations.

\begin{enumerate}
\item Define linear transformation
\item Is this a linear transformation?
\item Pick bases, representation with matrices
\item kernel, image (nullspace, columnspace), (one-to-one; onto),
  rank, nullity
\item The preimage of a vector is a linear combination of a vector in
  the null space and a particular solution.  Relate this to the
  general/specific breakdown of a solution to a system of equations.
\item inverse transformations/matrices.  Invertible matrix theorem.
\item change of basis matrix
\item If the basis is orthonormal, the inverse transformation (matrix)
  is $A^T$.
\item eigenvalues/eigenvectors---nice bases for linear
  transformations.  algebraic vs. geometric multiplicities.
\item composition of transformations/multiplication of matrices
  \begin{enumerate}
  \item an example problem might be showing that the $\rank(AB)\leq
    \min(\rank(A), \rank(B))$, see
    \href{http://www.math.ucsd.edu/~harel/Downloadable/The%20Linear%20Algebra%20Curriculum%20Study%20Group%20Recommendations%20-%20Moving%20Beyond%20Concept%20Definition.pdf}{LACSG article}, page 120, that the dimension of the image of $f\circ g \leq$ dimensions of the images of $f$ or $g$.

  \end{enumerate}
\item Symmetric matrices and spectral theorem, diagonalization
\end{enumerate}

\begin{problem}
  First Problem.
\end{problem}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "linear-algebra"
%%% End: 
